Output Summary

### 2023-04-18 03-post-process/output-plots-children/08-misc-process-model.Rmd
Update file names on output-plots children
Reorganize ocean survival & maturity  plots

```{r ocean-surv-plots, fig.width = 6, fig.height = 5}
ocean_surv_plot = function(j) {
  par(mfrow = c(3,2), oma = c(1.5,1.5,0,0))
  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
               main = TeX("$O_0 \\rightarrow O_1\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
               main = TeX("$O_0 \\rightarrow O_1\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
               main = TeX("$O_1 \\rightarrow O_2\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
               main = TeX("$O_1 \\rightarrow O_2\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)),
               main = TeX("$O_2 \\rightarrow O_3\\,(NOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)),
               main = TeX("$O_2 \\rightarrow O_3\\,(HOR)$"), yrs = all_yrs[ts_yrs], ylim = c(0,1))
  mtext(side = 1, outer = T, line = 0.5, "Brood Year")
  mtext(side = 2, outer = T, line = 0, "Survival")
}
```

### CAT

```{r}
ocean_surv_plot(j_cat)
```

### LOS

```{r}
ocean_surv_plot(j_los)
```

### MIN

```{r}
ocean_surv_plot(j_min)
```

### UGR

```{r}
ocean_surv_plot(j_ugr)
```

@@

```{r maturity-plot-fn}
maturity_plot = function(j) {
  par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
  plot_tseries(post_summ(post, sub_index("^psi_O1[year,origin,pop]$", year = ts_yrs, origin = o_nor, pop = j)), main = "Age 3 (NOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^psi_O1[year,origin,pop]$", year = ts_yrs, origin = o_hor, pop = j)), main = "Age 3 (HOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^psi_O2[year,origin,pop]$", year = ts_yrs, origin = o_nor, pop = j)), main = "Age 4 (NOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^psi_O2[year,origin,pop]$", year = ts_yrs, origin = o_hor, pop = j)), main = "Age 4 (HOR)", yrs = all_yrs[ts_yrs], ylim = c(0,1))

  mtext(side = 1, outer = T, line = 0.25, "Brood Year")
  mtext(side = 2, outer = T, line = 0.25, "Pr(Mature-at-Age|Alive in Ocean)")
}
```

### CAT

```{r maturity-cat, fig.width = 6, fig.height = 5}
maturity_plot(j_cat)
```

### LOS

```{r maturity-los, fig.width = 6, fig.height = 5}
maturity_plot(j_los)
```

### MIN

```{r maturity-min, fig.width = 6, fig.height = 5}
maturity_plot(j_min)
```

### UGR

```{r maturity-ugr, fig.width = 6, fig.height = 5}
maturity_plot(j_ugr)
```

>>>>

### Yr1 {.tabset .tabset-pills}

#### NOR {.tabset .tabset-pills}

##### Realized Alone

```{r phi-O0-O1-plots, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  keep = sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
  plot_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs], main = pops[j], ylim = c(0, 0.4))
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Yr1 Ocean Survival (NOR)")
```

##### Realized & [Predicted + AR(1)]

```{r phi-O0-O1-plots2, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  keep = sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
  plot_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs], main = pops[j], ylim = c(0, 0.4))

  keep = sub_index("^phi_O0_O1_dot2[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
  add_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Yr1 Ocean Survival (NOR)")
```

#### HOR {.tabset .tabset-pills}

##### Realized Alone

```{r phi-O0-O1-hor-plots, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  keep = sub_index("^phi_O0_O1[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
  plot_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs], main = pops[j], ylim = c(0, 0.4))
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Yr1 Ocean Survival (HOR)")
```

### Yr2 {.tabset .tabset-pills}

#### NOR

```{r phi-O1-O2-nor-plots, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  keep = sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
  plot_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs], main = pops[j], ylim = c(0, 1))
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Yr2 Ocean Survival (NOR)")
```

#### HOR

```{r phi-O1-O2-hor-plots, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  keep = sub_index("^phi_O1_O2[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
  plot_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs], main = pops[j], ylim = c(0, 1))
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Yr2 Ocean Survival (HOR)")
```

### Yr3 {.tabset .tabset-pills}

#### NOR

```{r phi-O2-O3-nor-plots, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  keep = sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
  plot_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs], main = pops[j], ylim = c(0, 1))
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Yr3 Ocean Survival (NOR)")
```

#### HOR

```{r phi-O2-O3-hor-plots, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  keep = sub_index("^phi_O2_O3[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
  plot_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs], main = pops[j], ylim = c(0, 1))
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Yr3 Ocean Survival (HOR)")
```

@@

### Pr(Age-3) {.tabset .tabset-pills}

#### NOR

```{r psi-O1-nor-plots, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  keep = sub_index("^psi_O1[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
  plot_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs], main = pops[j], ylim = c(0, 0.4))
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Pr(Mature Age-3|NOR)")
```

#### HOR

```{r psi-O1-hor-plots, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  keep = sub_index("^psi_O1[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
  plot_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs], main = pops[j], ylim = c(0, 0.4))
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Pr(Mature Age-3|HOR)")
```

### Pr(Age-4) {.tabset .tabset-pills}

#### NOR

```{r psi-O2-nor-plots, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  keep = sub_index("^psi_O2[year,origin,pop]", year = ts_yrs, origin = o_nor, pop = j)
  plot_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs], main = pops[j], ylim = c(0, 1))
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Pr(Mature Age-4|NOR)")
```

#### HOR

```{r psi-O2-hor-plots, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  keep = sub_index("^psi_O2[year,origin,pop]", year = ts_yrs, origin = o_hor, pop = j)
  plot_tseries(post_summ(post, keep), yrs = all_yrs[ts_yrs], main = pops[j], ylim = c(0, 1))
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Pr(Mature Age-4|HOR)")
```
